---
title: "Workflow Automation with Github Actions"
subtitle: ""  
author: "Ernest Guevarra"
date: '7 December 2021'
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: xaringan-themer.css
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      titleSlideClass: ["right", "bottom"]
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_mono_light(
  #base_color = "#509935",
  base_color = "#000000",
  base_font_size = "22px",
  title_slide_background_color = "#FFFFFF",
  title_slide_background_image = "images/ecohealth_title_background_4by3.png",
  title_slide_background_size = "contain",
  #title_slide_text_color = "#509935",
  title_slide_text_color = "#000000",
  background_image = "images/ecohealth_slide_background_4by3.png",
  header_font_google = google_font("Fira Sans"),
  text_font_google = google_font("Fira Sans Condensed"),
  code_font_google = google_font("Fira Mono"),
  code_font_size = "0.7rem",
  text_slide_number_font_size = "1em",
  link_color = "#509935"
)
```

### Outline

* Brief overview of **GitHub Actions**

* Using `targets` and `renv` within a containerised **GitHub Actions** workflow

* The `container-workflow-template` repository as a template for future projects

---

### GitHub Actions

* `GitHub Actions` allows **automation**, **customisation**, and **execution** of your research project workflows right in your GitHub repository.

* Composed of a job or a number of jobs. The job/s are then composed of steps that control the order in which actions are run in order to complete a job/s. This workflow is scheduled or triggered by a specific event and runs on what is called a runner - a server that has the GitHub Actions runner application installed - that is either hosted by GitHub, or self-hosted on your own machines.

* This whole workflow including the event trigger and the runner on which the workflow will run in are specified and detailed using a workflow .yml file that is saved inside a directory named .github within your GitHub repository in which you want to use GitHub Actions on.

---

background-image: url()
background-color: #FFFFFF

### GitHub Actions

<img src=https://miro.medium.com/max/2617/1*8mUtip6z_oydfLi4P86KUw.png />


---

class: center, middle

### Using `targets` and `renv` within a containerised **GitHub Actions** workflow

---

class: center, middle

# Questions?

---

class: center, middle

### The `container-workflow-template` repository as a template for future projects

---

class: center, middle

# Questions?

---

class: center, middle

# Thank you!

Slides can be viewed at https://ecohealthalliance.github.io/githubactions or PDF version downloaded at https://ecohealthalliance.github.io/githubactions/githubactions.pdf

R scripts for slides available at https://github.com/ecohealthalliance/githubactions

Repository for `container-workflow-template` at https://github.com/ecohealthalliance/container-workflow-template
